%-------------------------
% Resume for Cybersecurity Role
% Author : Ozirus Morency
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\Huge \scshape Ozirus B. Morency} \\ \vspace{1pt}
    \small Cybersecurity Analyst \\ \vspace{1pt}
    Fayetteville, GA \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ (201) 989-9502 ~ \href{mailto:ozirusmorency@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{ozirusmorency@gmail.com}} ~
    \href{https://linkedin.com/in/ozirus-morency}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/ozirusmorency}}  ~
    \href{https://github.com/ozzielove}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/ozzielove}}
    \vspace{-8pt}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
Entry-level cybersecurity professional pursuing B.S. in Cybersecurity with hands-on experience in security compliance, incident response, and risk management. Background in OSHA PSM and DHS CFATS regulatory frameworks. Google IT Support certified with skills in threat detection, access controls, and security documentation. Strong track record in audit support and compliance monitoring.

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Southern New Hampshire University}{Expected 2027}
      {Bachelor of Science in Cybersecurity, In Progress}{Manchester, NH}
      \resumeItemListStart
        \resumeItem{Relevant Coursework: Network security, threat analysis, security operations, incident response, risk management}
      \resumeItemListEnd
    \resumeSubheading
      {Union Catholic Regional High School}{September 2009 - June 2013}
      {High School Diploma}{Scotch Plains, NJ}
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Security Fundamentals}{: Threat detection, incident response, vulnerability assessment, access control, authentication, encryption basics} \\
     \textbf{Compliance \& Frameworks}{: OSHA PSM, DHS CFATS, EPA regulations, security audits, risk assessment, policy enforcement} \\
     \textbf{Security Operations}{: Log analysis, security monitoring, incident documentation, evidence collection, forensics basics} \\
     \textbf{Networking \& Systems}{: TCP/IP, DNS, DHCP, firewalls, VPN, intrusion detection concepts, network segmentation} \\
     \textbf{Operating Systems}{: Windows security, Linux hardening, user access management, patch management, system logs} \\
     \textbf{Tools}{: SIEM basics, ticketing systems (ServiceNow), asset management (DCIM/CMDB), antivirus, endpoint protection} \\
     \textbf{Data Security}{: Data classification, secure disposal, backup verification, chain of custody, audit logs} \\
     \textbf{Scripting \& Analysis}{: Bash, Python basics, SQL queries, log parsing, data analysis for security events} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------CERTIFICATIONS-----------
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Google IT Support Professional Certificate}{November 2025}
      {Coursera, Google Career Certificates}{coursera.org/verify/professional-cert/ZJM13OUEUNDM}
      \resumeItemListStart
        \resumeItem{Completed IT Security: Defense against the digital dark arts course covering encryption, AAA security, network hardening}
      \resumeItemListEnd
    \resumeSubheading
      {Google Data Analytics Professional Certificate}{November 2025}
      {Coursera, Google Career Certificates}{coursera.org/verify/professional-cert/XCRH44FAC62R}
    \resumeSubheading
      {Board-Certified Chemical Process Operator}{September 2023}
      {American Chemistry Council}{Safety and compliance in regulated environments}
    \resumeSubheading
      {U.S. Army Security Training}{March 2014}
      {U.S. Army Quartermaster Corps}{Anti-Terrorism, HazMat Safety, operational security}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Salute}{August 2025 - Present}
      {Data Center Technician}{Fayetteville, GA}
      \resumeItemListStart
        \resumeItem{Manage physical security for data center assets. Control access, verify credentials, escort vendors, and log all entry and exit activity.}
        \resumeItem{Track chain of custody for IT equipment. Scan assets, document transfers, photograph configurations, and maintain audit trails.}
        \resumeItem{Support security compliance through proper asset disposal. Follow data destruction procedures, document sanitization, and verify secure handling.}
        \resumeItem{Monitor access control systems. Review logs, report anomalies, and escalate security concerns to management.}
        \resumeItem{Maintain asset database security (DCIM/CMDB). Control user permissions, audit changes, and protect sensitive configuration data.}
        \resumeItem{Follow lockout/tagout procedures for equipment safety. Prevent unauthorized access to systems during maintenance.}
        \resumeItem{Document security incidents. Write detailed reports, collect evidence, and track remediation steps to closure.}
        \resumeItem{Support vendor security reviews. Verify background checks, validate scopes of work, and ensure compliance with security policies.}
      \resumeItemListEnd

    \resumeSubheading
      {Air Liquide}{December 2021 - August 2025}
      {Chemical Production Technician / Shift Lead}{Branchburg, NJ}
      \resumeItemListStart
        \resumeItem{Led security compliance for chemical facility under DHS CFATS regulations. Conducted security assessments, filed reports, and maintained 100\% compliance.}
        \resumeItem{Performed incident investigations for security and safety events. Analyzed root causes, documented findings, and tracked corrective actions.}
        \resumeItem{Managed access controls for restricted areas. Verified credentials, maintained logs, and reported unauthorized access attempts.}
        \resumeItem{Supported federal security audits. Prepared documentation, demonstrated controls, and addressed audit findings.}
        \resumeItem{Created security procedures and training materials. Wrote SOPs for access control, incident response, and emergency protocols.}
        \resumeItem{Conducted security drills with law enforcement and DHS. Tested response plans, identified gaps, and improved readiness scores to 98\%.}
        \resumeItem{Monitored production systems for anomalies. Detected unusual activity, investigated deviations, and prevented security incidents.}
        \resumeItem{Maintained hazardous material security per OSHA PSM requirements. Controlled inventory, tracked transfers, and prevented theft or misuse.}
      \resumeItemListEnd

    \resumeSubheading
      {Terminix}{February 2019 - December 2021}
      {Inspector \& Pest Control Technician}{New Jersey}
      \resumeItemListStart
        \resumeItem{Enforced EPA compliance for pesticide handling and storage. Maintained secure inventory, tracked usage, and prevented unauthorized access.}
        \resumeItem{Conducted risk assessments for 2,500+ properties. Identified vulnerabilities, documented findings, and recommended security improvements.}
        \resumeItem{Managed sensitive customer data securely. Protected personal information, followed privacy rules, and maintained confidentiality.}
        \resumeItem{Created compliance documentation for regulatory audits. Maintained logs, generated reports, and supported inspection reviews.}
      \resumeItemListEnd

    \resumeSubheading
      {U.S. Army National Guard}{July 2013 - July 2020}
      {Petroleum Supply Specialist (E-4)}{Westfield, NJ}
      \resumeItemListStart
        \resumeItem{Managed security for fuel operations and arms room. Controlled access, verified identities, and maintained 100\% accountability.}
        \resumeItem{Conducted fuel sampling for fraud investigations. Collected evidence, documented chain of custody, and supported CID cases.}
        \resumeItem{Completed Anti-Terrorism Level 1 training. Applied threat awareness, identified suspicious activity, and followed force protection measures.}
        \resumeItem{Maintained operational security (OPSEC) for logistics missions. Protected sensitive information and prevented disclosure of classified details.}
        \resumeItem{Earned 10 Army Achievement Medals for security compliance and mission success during multi-state and overseas operations.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\end{document}
